PANNEURO_analysis

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
Small fixes.

# Scoring for neuro measures (NOT INCLUDED)

# ALSfrs
```{r ALSfrs col names, include = FALSE}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

@@

```
# ESS
```{r ESS col names, include = FALSE}
ess.col.names <- dat.raw %>%
  select(
    starts_with("ess") & ends_with("numeric")
  ) %>%
  colnames()

@@

```{r ESS row sums, include = FALSE}
dat.raw <- dat.raw %>%
  mutate(ess.col.names =
   rowSums(select(.,ess.col.names), na.rm = F)
   )
```

```{r ESS frequencies, include=FALSE}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.col.names)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.col.names) %>%
  mutate(Prop = round(n/sum(n), 2))
```

@@

>>>>

# Scoring for neuro measures

# ALSfrs (not included)
```{r ALSfrs col names, include = FALSE}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

@@

@@

# ESS
```{r ESS col names, include = FALSE}
ess.col.names <- dat.raw %>%
  select(
    starts_with("ess") & ends_with("numeric")
  ) %>%
  colnames()

ess.col.names
```

```{r ESS row sums, include = FALSE}

# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
ess.items_key <- c(1,1,1,1,1,1,1,1)

# Create vector with items that are included in sum score
ess.items <- c(
  "ess.sitting_and_reading_numeric",
  "ess.watching_tv_numeric",
  "ess.sitting_inactive_in_a_public_place_numeric",
  "ess.break_passenger_car_hour_numeric",
  "ess.afternoon_rest_circumstances_lying_numeric",
  "ess.sitting_and_talking_to_someone_numeric",
  "ess.sitting_quietly_after_a_lunch_without_alcohol_numeric",
  "ess.car_minutes_stopped_traffic_numeric"
  )

# Calculate sum score
ess.scored_items <- scoreItems(keys = ess.items_key,
                                        items = dat.raw[ess.items],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
dat.raw$ess.sum_score_raw <- ess.scored_items$scores

# Look at values
dat.raw %>%
  group_by(covid_probable_case_incl_screening) %>% 
  descr(ess.sum_score_raw,
        stats = "common"
        )

```{r ESS raw score frequencies}
ess_frequencies <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.col.names)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sum_score_raw) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(ess_frequencies)
```

ESS scores: Interpretation
•	0 to 10 = normal range of sleepiness in healthy adults
•	11 to 14 = mild sleepiness
•	15 to 17 = moderate sleepiness
•	18 to 24 = severe sleepiness

```{r ess clinical categories}
dat.raw <- dat.raw %>% 
  mutate(ess.cutoff.scores =
           case_when(ess.col.names <= 10 ~ "Normal sleepiness",
                     ess.col.names > 10 & ess.col.names <= 14 ~ "Mild sleepiness",
                     ess.col.names > 14 & ess.col.names <= 17 ~ "Moderate sleepiness",
                     ess.col.names > 17 & ess.col.names <= 24 ~ "Severe sleepiness",
                     )
           )

```{r ESS clinical categories frequencies}
ess_frequencies <- dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.cutoff.scores)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.cutoff.scores) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(ess_frequencies)
```

@@

## Memory

```{r}
